R for Clinical Study Reports and Submission

### 2021-11-28 submission-package.Rmd
update adrg and arm tables with real-world formatting

The table below contains the software version and instructions
for executing the R analysis output programs:
```

| Software or Package                            | Version |
|------------------------------------------------|---------|
| R                                              | 4.1.1   |
| dplyr                                          | 1.0.7   |
| r2rtf                                          | 0.3.0   |
| pkglite                                        | 0.2.0   |
| ...                                            | ...     |
| R package versions based on CRAN at 2021-08-06 |         |

@@

+--------------------------------------+-------------+----------------------+-------------------------+---------------------------------------+
| Table Reference                      | Table Title | Programming Language | Program Name (programs) | Input File Name / Analysis (datasets) |
+======================================+=============+======================+=========================+=======================================+
| [Ref. x.y.z: P001ZZZ9999: Table 1-1] | ...         | R                    | tlf-01-disposition.txt  | adsl.xpt                              |
+--------------------------------------+-------------+----------------------+-------------------------+---------------------------------------+
| ...                                  | ...         | ...                  | ...                     | ...                                   |
+--------------------------------------+-------------+----------------------+-------------------------+---------------------------------------+

@@

|                                                       |                                                               |
|-------------------------------------------------------|---------------------------------------------------------------|
| Table Reference: [Ref. x.y.z: P001ZZZ9999: Table 1-1] | ...                                                           |
| Analysis Result                                       | ...                                                           |
| Analysis Parameters (s)                               | ...                                                           |
| Analysis Reason                                       | ...                                                           |
| Analysis Purpose                                      | ...                                                           |
| ...                                                   | ...                                                           |
| Programming Statements                                | (R version 4.1.1), [P001ZZZ9999: programs-tlf-01-disposition] |

>>>>

The tables below contain the software version and instructions
for executing the R analysis output programs:
```

```{r, echo=FALSE}
library("kableExtra")

df1 <- data.frame(
  program = c(
    "tlf-01-disposition.txt",
    "tlf-02-population.txt",
    "tlf-03-baseline.txt",
    "tlf-04-efficacy.txt",
    "tlf-05-ae-summary.txt",
    "tlf-06-ae-spec.txt"
  ),
  table = c(
    "Table x.y.z"
  ),
  desc = c(
    "Disposition of Patients",
    "Participants Accounting in Analysis Population (All Participants Randomized)",
    "Participant Baseline Characteristics (All Participants Randomized)",
    "ANCOVA of Change from Baseline Glucose (mmol/L) at Week 24 <br> LOCF <br> Efficacy Analysis Population",
    "Analysis of Adverse Event Summary (Safety Analysis Population)",
    "Analysis of Participants With Specific Adverse Events (Safety Analysis Population)"
  ),
  stringsAsFactors = FALSE
)

names(df1) <- c("Program Name", "Output Table", "Title")

df1 %>%
  kbl(escape = FALSE) %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 18) %>%
  column_spec(1, extra_css = "border: 1px solid #000; text-align: center;", width = "18rem") %>%
  column_spec(2, extra_css = "border: 1px solid #000; text-align: center;", width = "16rem") %>%
  column_spec(3, extra_css = "border: 1px solid #000;", width = "28rem") %>%
  row_spec(0, background = "#DFDFDF", bold = TRUE, extra_css = "border: 1px solid #000; text-align: center;")

df2 <- data.frame(
  package = c("pkglite", "haven", "dplyr", "tidyr", "emmeans", "r2rtf"),
  version = NA,
  description = c(
    "Prepare submission package",
    "Read SAS datasets",
    "Manipulate datasets",
    "Manipulate datasets",
    "Least-squares means estimation",
    "Create RTF tables"
  ),
  stringsAsFactors = FALSE
)

x <- available.packages(contriburl = contrib.url("https://mran.microsoft.com/snapshot/2021-08-06/"))
df2$version <- x[match(df2$package, x[, "Package"]), "Version"]

names(df2) <- c(
  "Open-Source R Analysis Package",
  "Package Version",
  "Analysis Package Description"
)

df2 %>%
  kbl() %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 18) %>%
  column_spec(1, extra_css = "border: 1px solid #000; text-align: center;", width = "18rem") %>%
  column_spec(2, extra_css = "border: 1px solid #000; text-align: center;", width = "16rem") %>%
  column_spec(3, extra_css = "border: 1px solid #000;", width = "28rem") %>%
  row_spec(0, background = "#DFDFDF", bold = TRUE, extra_css = "border: 1px solid #000; text-align: center;") %>%
  footnote(general = "R package versions based on CRAN on 2021-08-06", general_title = "")

df3 <- data.frame(
  package = "esubdemo",
  version = "0.1.0",
  description = "A demo package for analysis and reporting of clinical trials",
  stringsAsFactors = FALSE
)

names(df3) <- c(
  "Proprietary R Analysis Package",
  "Package Version",
  "Analysis Package Description"
)

df3 %>%
  kbl() %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 18) %>%
  column_spec(1, extra_css = "border: 1px solid #000; text-align: center;", width = "18rem") %>%
  column_spec(2, extra_css = "border: 1px solid #000; text-align: center;", width = "16rem") %>%
  column_spec(3, extra_css = "border: 1px solid #000;", width = "28rem") %>%
  row_spec(0, background = "#DFDFDF", bold = TRUE, extra_css = "border: 1px solid #000; text-align: center;")
```

@@

```{r, echo=FALSE}
df4 <- data.frame(
  "ref" = c("[Ref. x.y.z: P001ZZZ9999: Table 1-1]", "..."),
  "title" = c("Disposition of Patients", "..."),
  "pl" = c("R", "..."),
  "pn" = c("tlf-01-disposition.txt", "..."),
  "input" = c("adsl.xpt", "..."),
  stringsAsFactors = FALSE
)

names(df4) <- c(
  "Table Reference",
  "Table Title",
  "Programming Language",
  "Program Name (programs)",
  "Input File Name / Analysis (datasets)"
)

df4 %>%
  kbl() %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 18) %>%
  column_spec(1, extra_css = "border: 1px solid #000; text-align: center;") %>%
  column_spec(2, extra_css = "border: 1px solid #000; text-align: center;") %>%
  column_spec(3, extra_css = "border: 1px solid #000; text-align: center;") %>%
  column_spec(4, extra_css = "border: 1px solid #000; text-align: center;") %>%
  column_spec(5, extra_css = "border: 1px solid #000; text-align: center;") %>%
  row_spec(0, background = "#DFDFDF", bold = TRUE, extra_css = "border: 1px solid #000; text-align: center;")
```

@@

```{r, echo=FALSE}
df5 <- data.frame(
  "x1" = c(
    "Table Reference: [Ref. x.y.z: P001ZZZ9999: Table 1-1]",
    "Analysis Result",
    "Analysis Parameters (s)",
    "Analysis Reason",
    "Analysis Purpose",
    "...",
    "Programming Statements"
  ),
  "x2" = c(
    "...",
    "...",
    "...",
    "...",
    "...",
    "...",
    "(R version 4.1.1), [P001ZZZ9999: programs-tlf-01-disposition]"
  ),
  stringsAsFactors = FALSE
)

df5 %>%
  kbl(format = "html") %>%
  kable_classic(full_width = FALSE, html_font = "'Times New Roman', Times, serif", font_size = 18) %>%
  column_spec(1, extra_css = "border: 1px solid #000;", bold = TRUE) %>%
  column_spec(2, extra_css = "border: 1px solid #000;") %>%
  row_spec(0, background = "#DFDFDF", bold = TRUE, extra_css = "border: 1px solid #000;") %>%
  gsub("<thead>.*</thead>", "", .)
```
